Supplementary: A temporal network analysis of drug co-prescription around antidepressants and anxiolytics uses in the Netherlands from 2018 to 2022

### 2025-07-10 docs/abstract/_abstract-short.qmd
Finalize the first draft

**Methods:**
We utilized the IADB.nl database, including prescriptions from 128 Dutch pharmacies (2018–2022). A closed cohort of patients prescribed antidepressants/anxiolytics was extracted. Medications were classified using the Anatomical Therapeutic Chemical (ATC) system into 24 therapeutic classes. Time-varying DPNs were constructed as undirected graphs using symmetric daily dose-adjusted co-prescriptions. Eigenvector centrality ($c_e$) quantified relative nodal importance. Weekly-aggregated data included prescriptions ($n_c$), number of patients, claim-to-patient ratio, and eigenvector centrality. Singular spectrum analysis decomposed trends.

**Results:**
Antidepressants (ATC `N06A`, $c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics (`N05B`, $c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) had high eigenvector centrality, indicating frequent co-prescription. Additional high-centrality groups included medications for alimentary and metabolism (`A01-A16`), blood (`B01-B06`), cardiovascular (`C01-C10`), analgesics (`N02`), and respiratory (`R01-R07`).

**Discussion:**
DPNs reveal key polypharmacy patterns. High-centrality medications highlight potential targets for drug monitoring. This approach aids in identifying influential medications and refining prescribing oversight.

>>>>

**Methods:**
We utilized the IADB.nl database, including prescriptions from 128 Dutch pharmacies (2018–2022). A cohort of patients prescribed antidepressants/anxiolytics was extracted. Medications were classified using the Anatomical Therapeutic Chemical (ATC) system into 24 therapeutic classes. Time-varying DPNs were constructed as undirected graphs using symmetric daily dose-adjusted co-prescriptions. Eigenvector centrality ($c_e$) quantified relative nodal importance.  Weekly-aggregated data included prescriptions ($n_c$), number of patients, claim-to-patient ratio, and eigenvector centrality. Singular spectrum analysis decomposed trends.

**Results:**
Antidepressants ($c_e$: `r N06A$ce`, $n_c$: `r N06A$nc`) and anxiolytics ($c_e$: `r N05B$ce`, $n_c$: `r N05B$nc`) had high eigenvector centrality, demonstrating frequent co-prescription. Other ATC groups with high centrality included those for the alimentary tract and metabolism (`A01-A16`), blood and blood-forming organs (`B01-B06`), cardiovascular system (`C01-C10`), respiratory system (`R01-R07`), and analgesics (`N02`).

**Discussion:**
DPNs revealed key co-prescription patterns. High-centrality medications highlight potential targets for drug monitoring, such as identifying co-prescription trends that may warrant evaluation for safety, appropriateness, or policy oversight. This approach aids in identifying influential medications and refining prescribing oversight.

### 2025-07-10 docs/article.qmd
Finalize the first draft

format:
  elsevier-pdf:
    keep-tex: true
    keep-md: true
    include-in-header:
      file: _header.tex
    journal:
      formatting: review
      cite-style: authoryear
    output-file: iadb-network-analysis.pdf
  docx:
    pandoc-options: ["--mathml"]
    output-file: iadb-network-analysis.docx

@@

The inherently complex nature of health-related phenomena have fueled the growing implementation of network analysis, making it an important research framework in medicine and epidemiology [@Luke2007]. Past implementations of network analysis in public health mostly focused on transmission network, social network, and organizational network. Only recently, @Cavallo2012 demonstrated a novel framework to describe medication use on a population level, i.e. drug prescription network (DPN), a term which later is coined by @Bazzoni2015. Network analysis and graph theory offer an approach to model the relationship among building blocks of a complex system. From a complex system standpoint, polypharmacy is a prescription of multiple drug combinations which can be modelled as a network [@Miglio2021]. DPN can capture the complex relationships of a system that may vary over time, which is highly relevant to drugs prescribed for mental disorders.

In psychiatry, polypharmacy is defined as a patient with at least two concurrent psychiatric medications [@Shrivastava2013]. With a prevalence between 13-90%, psychiatric polypharmacy manifests in five categories, namely same-class, multi-class, adjunctive, augmentation, and total polypharmacy [@Shrivastava2013]. Same-class polypharmacy is the use of multiple medications from the same class. Multi-class polypharmacy is the use of multiple medications from different classes indicated for the same symptom cluster. Adjunctive polypharmacy is the use of additional medications to treat side effects due to other medications. Augmentation polypharmacy is the use of full-dose and sub-dose medications from a different class for the same symptom cluster. Finally, total polypharmacy is the overall number of medications a patient uses, including those prescribed for multiple psychiatric symptom clusters as well as for comorbid non-psychiatric conditions [@Shrivastava2013]. For policymakers, differences in defining polypharmacy pose a challenge to design an effective monitoring system [@Sirois2016]. Such monitoring is essential to identify prevalent co-prescription pattern that may impact treatment appropriateness and healthcare policy development.

@@

Node centrality measures, such as eigenvector centrality, quantify the importance of a medication in polypharmacy patterns [@Askar2021]. Addressing concerns about standardized polypharmacy indicators raised by @Sirois2016 and @Delara2022, we highlight eigenvector centrality as a key measure of a medication’s connection to highly prescribed drugs. A high eigenvector centrality suggests frequent co-prescription with commonly used medications, reflecting prescribing trends. Building on prior studies [@Cavallo2012; @Bazzoni2015], we hypothesize that eigenvector centrality serves as a meaningful quantitative indicator of polypharmacy. Therefore, this study aimed to assess the structural characteristics of temporal DPNs, focusing on the role of eigenvector centrality in identifying associated medications in adult patients prescribed for antidepressants or anxiolytics.

@@

Mathematically, a simple undirected graph $\mathcal{G}$ is a pair $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, where $\mathcal{V} = \left(1, \dots, n \right)$ is the set of nodes and $\mathcal{E} = \left(\{j, k\} \ | \ j, k \in \mathcal{V}, \ j \neq k \right)$ is the finite set of edges with $\{j, k\} = \{k, j\}$. The adjacency matrix $A \in \{0, 1\}^{n \times n}$ of a simple undirected graph $\mathcal{G}$ with $\mathcal{V}$ nodes is a square symmetric matrix of dimension $n \times n$ defined as @eq-graph-theory, with $A_{jk} = A_{kj}$ for all $j, k \in \mathcal{V}$ where $j \neq k$. For each day $t = \left(1, \dots, T \right)$ and each individual $p = \left(1, \dots, P \right)$, the adjacency matrix represented a simple undirected graph.

$$
A_{jk} = 
\begin{cases}
1 & \text{if } \{j, k\} \in \mathcal{E} \\
0 & \text{otherwise}
\end{cases}
$$ {#eq-graph-theory}

@@

A graph can be represented as an adjacency matrix $A$. The adjacency matrix $A$ has dimensions of $|\mathcal{V}| \times |\mathcal{V}|$, where $|\mathcal{V}|$ is the number of nodes in a graph. Each element of $A_{ij}$ is the edge, where in an unweighted graph, $A_{ij} = 1$ if a connection exists between $\mathcal{v}_i$ and $\mathcal{v}_j$, and $A_{ij} = 0$ otherwise. In a weighted graph, $A_{ij}$ can take any real value ($A_{ij} \in \mathbb{R}$) depending on the application [@estrada2012structure].

@@

The predomination of multi-class co-prescription among anxiolytics recipients is consistent with the recommendations in the Dutch Huisartsengenootschap [NHG; @NHG2019Anxiety]. Specifically, the NHG guideline for anxiety disorders advises short-term benzodiazepine use, limited to two to four weeks, as an adjunct to Selective Serotonin Reuptake Inhibitors (SSRIs) during treatment initiation. In contrast, the NHG guideline for depressive disorders recommends initiating pharmacotherapy with a single SSRI and discourages the combination of multiple antidepressants [@NHG2023Depression]. Therefore, the higher rate of multi-class co-prescription observed among anxiolytic users is consistent with evidence-based clinical practice, rather than an artifact of sampling or measurement methods.

>>>>

format:
  elsevier-pdf:
    keep-tex: true
    keep-md: true
    include-in-header:
      file: _header.tex
    journal:
      name: International Journal of Epidemiology
      formatting: review
      cite-style: numbername
    output-file: iadb-network-analysis.pdf
  docx:
    pandoc-options: ["--mathml"]
    output-file: iadb-network-analysis.docx

@@

The complexity of health-related phenomena has led to the growing application of network analysis in medicine and epidemiology [@Luke2007; @Miglio2021]. Graph theory provides the mathematical foundation for network analysis, offering an approach to study the relationships among the entities of a complex system. The early implementations of network analysis focused primarily on transmission, social, and organizational networks. More recently, @Cavallo2012 introduced drug prescription networks (DPNs) to model population-level drug prescription data. @Bazzoni2015 formalized the term, emphasizing its utility in understanding polypharmacy.

Psychiatric polypharmacy is defined as a patient with at least two concurrent psychiatric medications [@Shrivastava2013]. With a prevalence between 13-90%, psychiatric polypharmacy manifests in five categories, namely same-class, multi-class, adjunctive, augmentation, and total polypharmacy [@Shrivastava2013]. Same-class polypharmacy is the use of multiple medications from the same class. Multi-class polypharmacy is the use of multiple medications from different classes indicated for the same symptom cluster. Adjunctive polypharmacy is the use of additional medications to treat side effects due to other medications. Augmentation polypharmacy is the use of full-dose and sub-dose medications from a different class for the same symptom cluster. Finally, total polypharmacy is the overall number of medications a patient uses, including those prescribed for multiple psychiatric symptom clusters as well as for comorbid non-psychiatric conditions [@Shrivastava2013]. For policymakers, differences in defining polypharmacy pose a challenge to design an effective monitoring system [@Sirois2016]. Such monitoring is essential to identify prevalent co-prescription pattern that may impact treatment appropriateness and healthcare policy development.

@@

A DPN for an individual on a given day can be formalized as a simple undirected graph where medications correspond to nodes, and edges connecting pairs of nodes represent co-prescription relationships between medications [@Cavallo2012]. Typically, simple undirected graphs are represented by a square symmetric matrix with zeros on the diagonal called the adjacency matrix [@estrada2012structure]. In the adjacency matrix of the individual-level DPN, nonzero off-diagonal elements correspond to two medications being co-prescribed on a given day.

A population-level DPN on a given day can be constructed from individual-level DPNs through matrix addition of the corresponding adjacency matrices [@Cavallo2012]. A DPN at the population level on a given day is then formulated as a weighted undirected graph, which is characterized by a weighted adjacency matrix with weights equal to the counts of medication co-prescription occurrences. Therefore, analyzing the structural characteristics of a DPN over time using both local (medication-level) and global (network-level) graph measures offers valuable insights into co-prescription dynamics and can deepen our understanding of polypharmacy.

Local network statistics, such as node centrality measures, quantify the importance of a medication in polypharmacy patterns [@Askar2021]. Addressing concerns about standardized polypharmacy indicators raised by @Sirois2016 and @Delara2022, we highlight eigenvector centrality as a key measure of a medication’s connection to highly prescribed drugs. A high eigenvector centrality suggests frequent co-prescription with commonly used medications, reflecting prescribing trends. Building on prior studies [@Cavallo2012; @Bazzoni2015], we hypothesize that eigenvector centrality serves as a meaningful quantitative indicator of polypharmacy. Therefore, this study aimed to assess the structural characteristics of temporal DPNs, focusing on the role of eigenvector centrality in identifying associated medications in adult patients prescribed for antidepressants or anxiolytics.

@@

Mathematically, a simple undirected graph $\mathcal{G}$ is a pair $\mathcal{G} = (\mathcal{V}, \mathcal{E})$, where $\mathcal{V} = \left(1, \dots, n \right)$ is the set of nodes and $\mathcal{E} = \left(\{i, j\} \ | \ i, j \in \mathcal{V}, \ i \neq j \right)$ is the finite set of edges with $\{i, j\} = \{j, i\}$. The adjacency matrix $A \in \{0, 1\}^{n \times n}$ of a simple undirected graph $\mathcal{G}$ with $\mathcal{V}$ nodes is a square symmetric matrix of dimension $n \times n$ defined as @eq-graph-theory, with $A_{ij} = A_{ji}$ for all $i, j \in \mathcal{V}$ where $i \neq j$. For each day $t = \left(1, \dots, T \right)$ and each individual $p = \left(1, \dots, P \right)$, the adjacency matrix represented a simple undirected graph [@estrada2012structure].

$$
A_{ij} = 
\begin{cases}
1 & \text{if} \{i, j\} \in \mathcal{E} \\
0 & \text{otherwise}
\end{cases}
$$ {#eq-graph-theory}

@@

@@

The predomination of multi-class co-prescription among anxiolytics recipients is consistent with the recommendations in the Dutch College of General Practitioner (*Nederlands Huisartsen Genootschap*/NHG) [@NHG2019Anxiety]. Specifically, the NHG guideline for anxiety disorders advises short-term benzodiazepine use, limited to two to four weeks, as an adjunct to Selective Serotonin Reuptake Inhibitors (SSRIs) during treatment initiation. In contrast, the NHG guideline for depressive disorders recommends initiating pharmacotherapy with a single SSRI and discourages the combination of multiple antidepressants [@NHG2023Depression]. Therefore, the higher rate of multi-class co-prescription observed among anxiolytic users is consistent with evidence-based clinical practice, rather than an artifact of sampling or measurement methods.

### 2025-07-10 docs/exec-summary/_preprocessing.qmd
Finalize the first draft

At the individual level, each patient's daily prescription record at time $t$ was encoded into a square matrix $A_t^{(i)}$, where rows and columns represent medication classes according to the ATC classification. An off-diagonal entry $A_{t_{jk}}^{(i)} = 1$ indicates that medication classes $j$ and $k$ were co-prescribed on the same day for individual $i$, while a diagonal entry $A_{t_{jj}}^{(i)} = 1$ captures the presence of a single prescription of medication $j$. To derive the population-level DPN, all individual-level daily prescription matrix $A^{(i)}$ were aggregated by computing their element-wise sum.

$$A_t = \displaystyle \sum_i A_t^{(i)}$$ {#eq-DPN}

The population matrix $A_t$ captures the frequency of co-prescriptions (off-diagonal) and single prescriptions (diagonal) across the dataset at the specified time $t$. Each element $A_{t_{jk}}$ in the matrix was interpreted as the number of patients being prescribed with medication classes $j$ and $k$ on the same day $t$. $A_t$ was represented as a weighted undirected graph, where each node corresponds to a medication class and edges reflect co-prescription frequencies. In the original work of DPN, all defined daily dose (DDD) were assumed equal to 1, allowing for applying raw counts as the edge weights. However, since not all medications have DDD = 1, this assumption could lead to inaccurate representations. To enhance the accuracy of edge weights, we introduced a weighting function to adjust the contribution of each co-prescription. Specifically, each co-prescribed medication class was assigned a weight $\omega_j$ based on its DDD value using a Gaussian kernel centered at the baseline weight $\omega_B = 1$, i.e., the expected DDD, with standard deviation $\sigma = \frac{1}{3}$ to allow for a gradual reduction in weight as DDD deviates from 1.

@@

The edge weight between medication classes $j$ and $k$ was computed as the average of their individual weights:

>>>>

At the individual level, each patient's daily prescription record at time $t$ was encoded into a square matrix $A_t^{(p)}$, where rows and columns represent medication classes according to the ATC classification. An off-diagonal entry $A_{t_{ij}}^{(p)} = 1$ indicates that medication classes $i$ and $j$ were co-prescribed on the same day for individual $p$, while a diagonal entry $A_{t_{ii}}^{(p)} = 1$ captures the presence of a single prescription of medication $i$. To derive the population-level DPN, all individual-level daily prescription matrix $A^{(p)}$ were aggregated by computing their element-wise sum.

$$A_t = \displaystyle \sum_i A_t^{(p)}$$ {#eq-DPN}

The population matrix $A_t$ captures the frequency of co-prescriptions (off-diagonal) and single prescriptions (diagonal) across the dataset at the specified time $t$. Each element $A_{t_{ij}}$ in the matrix was interpreted as the number of patients being prescribed with medication classes $i$ and $j$ on the same day $t$. $A_t$ was represented as a weighted undirected graph, where each node corresponds to a medication class and edges reflect co-prescription frequencies. In the original work of DPN, all defined daily dose (DDD) were assumed equal to 1, allowing for applying raw counts as the edge weights. However, since not all medications have DDD = 1, this assumption could lead to inaccurate representations. To enhance the accuracy of edge weights, we introduced a weighting function to adjust the contribution of each co-prescription. Specifically, each co-prescribed medication class was assigned a weight $\omega_j$ based on its DDD value using a Gaussian kernel centered at the baseline weight $\omega_B = 1$, i.e., the expected DDD, with standard deviation $\sigma = \frac{1}{3}$ to allow for a gradual reduction in weight as DDD deviates from 1.

@@

The edge weight between medication classes $i$ and $j$ was computed as the average of their individual weights:

### 2025-07-10 docs/supplementary.qmd
Finalize the first draft

format:
  pdf:
    keep-tex: true
    include-in-header:
      - file: _header.tex
      - text: |
          \renewcommand*{\thesection}{S\arabic{section}}
    output-file: iadb-network-analysis-supplementary.pdf
    number-sections: true
    number-depth: 3
    geometry:
      - inner=2cm
      - outer=3cm
      - top=2cm
      - bottom=2.5cm
  docx:
    pandoc-options: ["--mathml"]
    output-file: iadb-network-analysis-supplementary.docx

@@

@@

```{r}
#| fig-width: 16
#| fig-height: 9
#| fig-pos: H
#| fig-cap: Time-series decomposition using singular spectrum analysis-based approach

@@

>>>>

format:
  pdf:
    keep-tex: true
    include-in-header:
      - file: _header.tex
      - text: |
          \renewcommand*{\thesection}{S\arabic{section}}
    output-file: iadb-network-analysis-supplementary.pdf
    number-sections: true
    number-depth: 3
    geometry:
      - inner=2cm
      - outer=3cm
      - top=2cm
      - bottom=2.5cm

@@

```{r}
#| fig-width: 14
#| fig-height: 8
#| fig-cap: Reconstructed time series data using the SSA-based approach

tar_read(plt_dot_recon_n_claim)
tar_read(plt_dot_recon_eigen)

@@

```{r tbl-trend}
#| tbl-cap: Trend of medication uses alongside its measure of relative importance

prettyRound <- function(x, ...) {
  x %<>% round(...) %>% {ifelse(. == 0, "<0.001", as.character(.))}
}

fnote <- "The statistics were obtained from Mann-Kendall trend test, where positive result signifies a positive slope"

tar_read(decom_ssa) %>%
  subset(.$component %in% c("Original", "Trend") & .$metric != "claim2patient") %>%
  tibble::tibble() %>%
  dplyr::group_by(metric, group, component) %>%
  dplyr::group_modify(~trend::mk.test(.x$value) %>% broom::tidy()) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    "Mann-Kendall" = sprintf(
      "%s (p %s)", prettyRound(statistic, 2), prettyRound(p.value, 3)
    )
  ) %>%
  subset(select = -c(statistic:alternative)) %>%
  tidyr::pivot_wider(names_from = metric, values_from = `Mann-Kendall`) %>%
  tidyr::pivot_wider(names_from = component, values_from = eigen:n_claim) %>%
  set_colnames(c("ATC Group", rep(c("Original", "Trend"), 2))) %>%
  knitr::kable(longtable = TRUE, booktabs = TRUE) %>%
  kableExtra::kable_styling(latex_options = "repeat_header") %>%
  kableExtra::add_header_above(c(" " = 1, "Eigenvector Centrality" = 2, "Prescription Dispensing" = 2)) %>%
  kableExtra::add_footnote(fnote, notation = "none")

```{r}
#| fig-width: 16
#| fig-height: 9
#| fig-pos: H
#| fig-cap: Time-series decomposition using singular spectrum analysis-based approach
#| eval: FALSE

@@

tar_read(plt_ssa_recon_eigen)[[1]]
tar_read(plt_ssa_recon_eigen)[[2]]
tar_read(plt_ssa_recon_eigen)[[3]]
tar_read(plt_ssa_recon_eigen)[[4]]
tar_read(plt_ssa_recon_eigen)[[5]]
tar_read(plt_ssa_recon_eigen)[[6]]
tar_read(plt_ssa_recon_eigen)[[7]]
tar_read(plt_ssa_recon_eigen)[[8]]
tar_read(plt_ssa_recon_eigen)[[9]]
tar_read(plt_ssa_recon_eigen)[[10]]
tar_read(plt_ssa_recon_eigen)[[11]]
tar_read(plt_ssa_recon_eigen)[[12]]
tar_read(plt_ssa_recon_eigen)[[13]]
tar_read(plt_ssa_recon_eigen)[[14]]
tar_read(plt_ssa_recon_eigen)[[15]]
tar_read(plt_ssa_recon_eigen)[[16]]
tar_read(plt_ssa_recon_eigen)[[17]]
tar_read(plt_ssa_recon_eigen)[[18]]
tar_read(plt_ssa_recon_eigen)[[19]]
tar_read(plt_ssa_recon_eigen)[[20]]
tar_read(plt_ssa_recon_eigen)[[21]]
tar_read(plt_ssa_recon_eigen)[[22]]
tar_read(plt_ssa_recon_eigen)[[23]]
tar_read(plt_ssa_recon_eigen)[[24]]

### 2025-07-10 docs/supplementary.tex
Finalize the first draft

\usepackage{longtable}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{float}
\usepackage{typearea}
\floatplacement{figure}{htbp}
\floatplacement{table}{htbp}
\AtBeginDocument{%
  \storeareas\normalpapersize
}
\BeforeRestoreareas{\cleardoublepage}
\newcommand*\uselandscape{%
  \cleardoublepage
  \KOMAoptions{paper=landscape}%
  \recalctypearea
  \areaset{1.2\textwidth}{1.2\textheight}%
}
\renewcommand*{\thesection}{S\arabic{section}}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

@@

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-3.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-4.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-5.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-6.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-7.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-8.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-9.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-10.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-11.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-12.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-13.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-14.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-15.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-16.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-17.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-18.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-19.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-20.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-21.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-22.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

{\centering \includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{supplementary_files/figure-pdf/unnamed-chunk-2-23.pdf}

\caption{Time-series decomposition using singular spectrum
analysis-based approach}

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{multicol}
\usepackage{float}
\usepackage{typearea}
\floatplacement{figure}{htbp}
\floatplacement{table}{htbp}
\AtBeginDocument{%
  \storeareas\normalpapersize
}
\BeforeRestoreareas{\cleardoublepage}
\newcommand*\uselandscape{%
  \cleardoublepage
  \KOMAoptions{paper=landscape}%
  \recalctypearea
  \areaset{1.2\textwidth}{1.2\textheight}%
}
\renewcommand*{\thesection}{S\arabic{section}}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\caption{Reconstructed time series data using the SSA-based approach}

@@

\begin{longtable}{lllll}

\caption{\label{tbl-trend}Trend of medication uses alongside its measure
of relative importance}

\tabularnewline

\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Eigenvector Centrality} & \multicolumn{2}{c}{Prescription Dispensing} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
ATC Group & Original & Trend & Original & Trend\\
\midrule
\endfirsthead
\multicolumn{5}{@{}l}{\textit{(continued)}}\\
\toprule
ATC Group & Original & Trend & Original & Trend\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
Alimentary and metabolism & 18.63 (p <0.001) & 24.05 (p <0.001) & 11.11 (p <0.001) & 23.8 (p <0.001)\\
Blood & 17.02 (p <0.001) & 24.06 (p <0.001) & 13.24 (p <0.001) & 24.02 (p <0.001)\\
Cardiovascular & 18.11 (p <0.001) & 24.06 (p <0.001) & 14.39 (p <0.001) & 23.19 (p <0.001)\\
Dermatologicals & 3.47 (p 0.001) & 9.83 (p <0.001) & -0.1 (p 0.919) & -2.54 (p 0.011)\\
Genitourinary & -0.37 (p 0.714) & -1.27 (p 0.204) & -3 (p 0.003) & -11.57 (p <0.001)\\
\addlinespace
Systemic hormonal & -11.44 (p <0.001) & -20.17 (p <0.001) & 5.36 (p <0.001) & 13.01 (p <0.001)\\
Systemic anti-infectives & -7.25 (p <0.001) & -12.64 (p <0.001) & -7.3 (p <0.001) & -12.25 (p <0.001)\\
Antineoplastics & 1.22 (p 0.224) & 3.58 (p <0.001) & 8.86 (p <0.001) & 18.52 (p <0.001)\\
Musculoskeletal & -6.92 (p <0.001) & -13.76 (p <0.001) & -6.6 (p <0.001) & -14.98 (p <0.001)\\
Anesthetic & -1.27 (p 0.204) & -10.01 (p <0.001) & -8.17 (p <0.001) & -19.57 (p <0.001)\\
\addlinespace
Analgesics & -14.12 (p <0.001) & -22.7 (p <0.001) & -2.97 (p 0.003) & -4.62 (p <0.001)\\
Antiepileptics & -15.08 (p <0.001) & -24.07 (p <0.001) & -7.31 (p <0.001) & -17.78 (p <0.001)\\
Antiparkinson & -9.09 (p <0.001) & -23.07 (p <0.001) & 4.27 (p <0.001) & 18.66 (p <0.001)\\
Antipsychotics & -9.36 (p <0.001) & -17.68 (p <0.001) & 6.51 (p <0.001) & 18.26 (p <0.001)\\
Anxiolytics & -13.49 (p <0.001) & -20.76 (p <0.001) & -4.77 (p <0.001) & -9.75 (p <0.001)\\
\addlinespace
Hypnotics and sedatives & -16.68 (p <0.001) & -24.06 (p <0.001) & 0.13 (p 0.898) & 0.58 (p 0.563)\\
Antidepressants & 8.06 (p <0.001) & 15.65 (p <0.001) & 9.43 (p <0.001) & 21.52 (p <0.001)\\
Psychostimulants & 11.2 (p <0.001) & 23.93 (p <0.001) & 13.75 (p <0.001) & 23.85 (p <0.001)\\
Antidementia & -0.71 (p 0.477) & -4.24 (p <0.001) & 2.57 (p 0.01) & 1.43 (p 0.153)\\
Other nervous system drugs & -7.97 (p <0.001) & -6.6 (p <0.001) & -5.85 (p <0.001) & -6.96 (p <0.001)\\
\addlinespace
Antiparasitics & 0.38 (p 0.706) & 7.99 (p <0.001) & 4.81 (p <0.001) & 13.23 (p <0.001)\\
Respiratory & -2.57 (p 0.01) & -5.72 (p <0.001) & -0.28 (p 0.778) & -3.53 (p <0.001)\\
Sensory & 12.14 (p <0.001) & 21.08 (p <0.001) & 8.15 (p <0.001) & 23.46 (p <0.001)\\
Others & -0.87 (p 0.385) & 3.77 (p <0.001) & -12.18 (p <0.001) & -14.55 (p <0.001)\\*

\end{longtable}
